Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-18 docs/questioning.tex
Change of definitions + requirements

@@

An intrusion detection system examines some software artifact and
reports vulnerabilities. The value an intrusion detection system can
be measured in terms of its \emph{accuracy}, which gauges the quality
of its output. An intrusion detection system makes predictions for
vulnerabilities. The following may happen:
\begin{itemize}
\item A prediction about a vulnerability is true. That is a \emph{true
    positive}. 
\item A prediction about a vulnerability is false; intrusion
  detection reported something that in reality is not vulnerability.
  That is a \emph{false positive}.
\item A prediction about the absence of a vulnerability is true. That
  is a \emph{true negative}: intrusion detection evaluated something
  as being safe, and it is.
\item A prediction about the absence of a vulnerability is false. That
  is a \emph{false negative}: intrusion detection missed a
  vulnerability.
\end{itemize}
In terms of the above, the \emph{Positive Predictive Value} (PPV) is
defined as the ratio of true positives over all reported positives,
while the \emph{Negative Predictive Value} (NPV) is defined as the
ratio of true negatives over all reported negatives. In intrusion
detection, the PPV is an indicator of how much we should be worried
about a reported vulnerability being true. Conversely, the NPV is an
indicator of how much we should be reassured when no vulnerabilities
are reported.

>>>>

The evaluation of

\section{Analysis Dimensions}

\begin{itemize}
\item {\bf Sensitivity}, the probability that an attack will be
  caught.
\item {\bf Specificity}, the probability that a normal interaction
  will test negative.
\item {\bf Positive Predictive Value} (PPV), the probability that a
  reported attack is a real attack.
\item {\bf Negative Predictive Value} (NPV), the probability that if
  nothing is reported no attack has taken place.
\end{itemize}

To do any meaningful calculation of the above, we need to define
precisely the following in our methodology:
\begin{itemize}
\item True Positive (TP)
\item False Positive (FP)
\item True Negative (TN)
\item False Negative (FN)
\end{itemize}

@@

An intrusion detection system examines some software artifact and
reports vulnerabilities. The value an intrusion detection system can
be measured in terms of its \emph{accuracy}, which gauges the quality
of its output. An intrusion detection system:
\begin{itemize}
\item A prediction about a vulnerability is true. That is a \emph{true
    positive}. 
\item A prediction about a vulnerability is false; intrusion
  detection reported something that in reality is not vulnerability.
  That is a \emph{false positive}.
\item A prediction about the absence of a vulnerability is true. That
  is a \emph{true negative}: intrusion detection evaluated something
  as being safe, and it is.
\item A prediction about the absence of a vulnerability is false. That
  is a \emph{false negative}: intrusion detection missed a
  vulnerability.
\end{itemize}
In terms of the above, the \emph{Positive Predictive Value} (PPV) is
defined as the ratio of true positives over all reported positives,
while the \emph{Negative Predictive Value} (NPV) is defined as the
ratio of true negatives over all reported negatives. In intrusion
detection, the PPV is an indicator of how much we should be worried
about a reported vulnerability being true. Conversely, the NPV is an
indicator of how much we should be reassured when no vulnerabilities
are reported.
